---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# bibler

<!-- badges: start -->
<!-- badges: end -->

The goal of the bibler package is to enable the analyst to use and improve their skills while enhancing their Bible Study time.

## Installation

bibler is not on CRAN yet but you can download the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("benrwoodard/bibler")
```

## Authentication

The bibler package relies on the [API.Bible](https://scripture.api.bible/) project. I honestly do not know much about it other than what I have read on [the welcome page](https://docs.api.bible/).  I went through several different iterations in the development of the package and finally settled on this API because of the simplicity and solid documentation. 

**Current Process**
In order to pull any data from the API you will need to signup for an account. 

1. Register as a Developer

The first step to get access to API.Bible is to register as a developer. Fill out and submit the form at https://scripture.api.bible/signup.

Once you submit the form, you will receive an email with a link to verify your email address. You will be able to sign in to your account after verifying your email. If you don't see the email, be sure to check your spam folder.

2. Create your App

Once you have an account, create your app by going to https://scripture.api.bible/admin/applications/new. You should be taken there automatically the first time you login to your account. After submitting your application, you must wait for it to be approved.

When you create an app, you are also applying for an API key. Give as much information as possible to make it more likely your app will be approved."

3. Add the API Key

Once you have been approved you can go into your account and copy the API key. You can either use this in very function as an argument, `apikey = `, or add it to the .Renviron* file (recommended).  Once added to the .Renviron file using the variable name  `BIBLER_APIKEY` you need to **restart your R session**.  

Now you are ready to being pulling data from the API.

*For more information about the .Renviron file, [go here](http://www.dartistics.com/renviron.html).

## Examples

Here are some basic functions you an use to get started:

1. Pull a list of all available bibles

```{r example}
library(bibler)

bibles_list <- bibles(language = 'eng', name = 'king james')

bibles_list
```
This result will show you all the different translations with the phrase 'king james' in the `name`.  I recommend copying the id of your main version and adding that to the .Renviron file for quicker function calls.  The package is developed to reference the API key and main Bible Id using the .Renviron file.  Add `MAIN_BIBLEID` as a variable in the file and restart the R session.  

2. Search to find a word or phrase you have been looking for.

```{r}
bible_search(query = 'moses held')



```

